\documentclass[12pt]{amsart} 
      % \newif\ifpreview
      % \previewfalse
% approx iid
\newcommand\simiid{\stackrel{\mathclap{\normalfont\mbox{\tiny{iid}}}}{\sim}}\usepackage{natbib}

% Fonts
\usepackage[default,osfigures,scale=0.95]{opensans}
\usepackage[T1]{fontenc}
\usepackage{ae}

% easy commands for number propers
\newcommand{\first}{1$^{\text{st}}$}
\newcommand{\second}{2$^{\text{nd}}$}
\newcommand{\third}{3$^{\text{rd}}$}
\newcommand{\nth}[1]{${#1}^{\text{th}}$}

% Generate some fake text
\usepackage{blindtext}

% % add watermark
% \usepackage{draftwatermark}
% \SetWatermarkText{Draft: Not Ready}
% \SetWatermarkScale{.5}
% \SetWatermarkColor[gray]{0.9}

% layout control
\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1.25in,lmargin=1in,rmargin=1in}
\usepackage{parallel}
\usepackage{parcolumns}
\usepackage{fancyhdr}
\usepackage[export]{adjustbox}
\usepackage{etoolbox}

% math typesetting
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{relsize}
\usepackage{mathtools}
\usepackage{bm}
%\usepackage[%decimalsymbol=.,digitsep=fullstop]{siunitx}

% restricts float objects to be inserted before end of section
% creates float barriers
\usepackage[section]{placeins}

% tables
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{longtable}

% to adapt caption style
\usepackage[font={small},labelfont=bf]{caption}

% footnotes at bottom
%\usepackage[bottom]{footmisc}

% to change enumeration symbols begin{enumerate}[(a)]
\usepackage{enumerate}
\usepackage{paralist}

% to colorize links in document. See color specification below
\usepackage[pdftex,hyperref,x11names]{xcolor}

% for multiple references and insertion of the word "figure" or "table"
% \usepackage{cleveref}

% load the hyper-references package and set document info
\usepackage[pdftex]{hyperref}

% graphics stuff
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage[space]{grffile} % allows us to specify directories that have spaces
\usepackage{placeins} % prevents floats from moving past a \FloatBarrier
\usepackage{tikz}

% sideway figures
\usepackage{rotating}
\usepackage{lscape}

%\usepackage[figuresright]{rotating}
% \newenvironment{amssidewaysfigure}  {\begin{sidewaysfigure}\vspace*{.8\textwidth}\begin{minipage}{\textheight}\centering}
%   {\end{minipage}\end{sidewaysfigure}}

% Spacing
\usepackage[doublespacing]{setspace}

% define clickable links and their colors
\hypersetup{%
	unicode=false,          % non-Latin characters in Acrobat's bookmarks
	pdftoolbar=true,        % show Acrobat's toolbar?
	pdfmenubar=true,        % show Acrobat's menu?
	pdffitwindow=false,     % window fit to page when opened
	pdfstartview={FitH},    % fits the width of the page to the window
	pdfnewwindow=true,%
	%pagebackref=false,%
	pdfauthor={Shahryar Minhas, et alia.},%
	pdftitle={How to Fix IR},%
	colorlinks,%
	citecolor=black,%
	filecolor=black,%
	linkcolor=black,%
	urlcolor=RoyalBlue4
}

% -------------------- title -------------------- %

\title{International Relations are a Social Network:\\ A Latent Network Approach for Global Politics}
\vspace{\baselineskip}

 \author[Minhas]{Shahryar Minhas}
 \address{Shahryar Minhas: Department of Political Science}
 \curraddr{Michigan State University}
 \email[Corresponding author]{minhassh@msu.edu}

 \author[Dorff]{Cassy L. Dorff}
 \address{Cassy L. Dorff}
 \curraddr{Department of Political Science, University of New Mexico}
 \email{cdorff@unm.edu}

 \author[Foster]{Margaret Foster}
 \address{Margaret Foster}
 \curraddr{Department of Political Science, Duke University}
 \email{margaret.foster@duke.edu}
 
 \author[Gallop]{Max Gallop}
 \address{Max Gallop}
 \curraddr{Department of Government and Public Policy, University of Strathclyde}
 \email{max.gallop@strath.ac.uk}
 
  \author[Liu]{Howard Liu}
 \address{Howard Liu}
 \curraddr{Department of Political Science, Duke University}
 \email{hao.liu@duke.edu}

 \author[Tellez]{Juan Tellez}
 \address{Juan Tellez}
 \curraddr{Department of Political Science, Duke University}
 \email{juan.tellez@duke.edu}

\author[Ward]{Michael D. Ward}
\address{Michael D. Ward}
\curraddr{Department of Political Science, Duke University}
\email{michael.d.ward@duke.edu}

% \date{\today}

\thanks{Shahryar Minhas and Michael D. Ward acknowledge support from National Science Foundation (NSF) Award 1259266. Robert Franzese provided welcome and helpful comments on the broader project from which this effort emerges at the 2017 Summer Political Methodology Meetings. We also thank Douglas Gibler, of the University of Alabama, for kindly providing us with a copy of the data and programs he used in \citet{gibler:2017}.}

\setlength{\headheight}{15pt}
\setlength{\headsep}{20pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{\fancyplain{}{}}
\chead{\fancyplain{}{How to fix IR}}
\rhead{\fancyplain{}{\today}}
\rfoot{\fancyplain{}{\thepage}}
% references to graphics
\makeatletter
% let's keep them in the same directory \def\input@path{{}

% easy command for boldface math symbols
\newcommand{\mbs}[1]{\boldsymbol{#1}}

% command for R package font
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

% Add some colors
\definecolor{red1}{RGB}{253,219,199}
\definecolor{red2}{RGB}{244,165,130}
\definecolor{red3}{RGB}{178,24,43}

\definecolor{green1}{RGB}{229,245,224}
\definecolor{green2}{RGB}{161,217,155}
\definecolor{green3}{RGB}{49,163,84}

\definecolor{blue0}{RGB}{255,247,251}
\definecolor{blue1}{RGB}{222,235,247}
\definecolor{blue2}{RGB}{158,202,225}
\definecolor{blue3}{RGB}{49,130,189}
\definecolor{blue4}{RGB}{4,90,141}

\definecolor{purple1}{RGB}{191,211,230}
\definecolor{purple2}{RGB}{140,150,198}
\definecolor{purple3}{RGB}{140,107,177}

\definecolor{brown1}{RGB}{246,232,195}
\definecolor{brown2}{RGB}{223,194,125}
\definecolor{brown3}{RGB}{191,129,45}

% square bracket matrices
\let\bbordermatrix\bordermatrix
\patchcmd{\bbordermatrix}{8.75}{4.75}{}{}
\patchcmd{\bbordermatrix}{\left(}{\left[}{}{}
\patchcmd{\bbordermatrix}{\right)}{\right]}{}{}


\begin{document}
      % \ifpreview {
      %    \definecolor{personal}{rgb}{1.0, 1.0, 0.0}
      %    \pagecolor{personal}
      %    }
      % \fi

\small{\singlespacing{
\begin{abstract}
	International relations scholarship is filled with dyads. This includes dyadic hypotheses and propositions, but especially data.  These relational data contain information about the interdependencies of various phenomena, including countries, dyads, and even triads.  However, most empirical studies of such data do not take into account these dependencies. As a result, the studies are often contradictory and produce results that are not compelling. One reason is that the independence required by the typical methods employed does not exist in the data being studied.  We present a different, regression based method, which constructs a latent network which incorporates \first, \second, and \third-order dependencies. We replicate five prominent studies in recent IR scholarship and compare the standard approach to the latent factor approach. The additive and multiplicative latent factor approach is shown to produce more precise estimates of covariate effects, and it also dominates standard approaches in terms of out-of-sample cross-validations.
\end{abstract}
}}

\maketitle\thispagestyle{empty}
\newpage\setcounter{page}{1} 

\input{1_intro}
\input{2_model}
\input{3_sim}
\input{4_app}
\input{5_concl}
\input{6_appendix}

%%What about a summary table with AUCs for the different network models here? - MG
\newpage
% Bib stuff
\clearpage
% \bibliography{master.bib}
\bibliography{/Users/s7m/whistle/master}
\bibliographystyle{authordate1}
% \clearpage
% \section*{All About Us}

\end{document} 